humanCdGF_predict_cfu

### 2016-11-07 code/HumanCdGF_predict_cfu.Rmd
remove old col rate code

```{r predict colonization rate, fig.width=10,fig.height=10}
# plot initial C. difficile colonization of mice 
#meta_data %>% 
#  filter(day %in% c(1,2,3,4), !cage_id == 'NP1', 
#         Early_Euth == FALSE, cdiff_strain == 431) %>% 
#  ggplot(aes(x = factor(day), y = log_cfu, color = cage_id)) + 
#    geom_line(aes(group = mouse_id), size=.25, alpha=0.4) + geom_point() +
#    stat_summary(fun.y=mean, geom="line", aes(group = cage_id)) + 
#    theme_bw() + labs(x = 'Day', y = 'C Diff CFU (log10)') +
#   theme(legend.justification=c(1,0), legend.position=c(1,0), 
#          legend.title=element_blank())

@@

#top_col_rate_df <- data.frame(shared_colonized.df %>% 
#  select(ratio, one_of(cr_features)) %>% 
#  left_join(col_rate))

#set.seed(seed)
#rf_col_rate_features <- randomForest(ratio ~ ., data=top_col_rate_df,
#                              importance=TRUE, ntree=n_trees, mtry = 2,
#                              keep.forest=TRUE)
#importance_final <- sort(importance(rf_col_rate_features)[,1], decreasing = T)
#rf_col_rate_prediction <- data.frame(observed = shared_colonized.df$ratio, 
#                       predicted = rf_col_rate_features$predicted)
#rf_cr_prediction <- cbind(cage_id = shared_col_rate.df[,'cage_id'], rf_col_rate_prediction)

@@

#importance.df <- data.frame(otu = names(importance_final),
#                            importance = importance_final,
#                            get_tax(1, names(importance_final), tax_file))

>>>>

```{r predict colonization rate, fig.width=10,fig.height=10}

@@

@@
